Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-03 talk/dls2014/paper/paper.tex
Add a paragraph 'if we're not on x86 then'

>>>>

If support for this is not available (due to the compiler or on a
different architecture), there are other optimizations possible.  For
example, using gcc, a regular register can be globally reserved and
all ``simple enough'' memory accesses will still resolve to a single
instruction.  More complicated accesses, e.g.\ those involving array
indexing, will need an extra explicit addition.
